MultiDataProcessPico

### 2023-12-07 Code/MultiDataProcessPico.Rmd
Moved to load tidyverse after all other packages to avoid discrepencies.

```{r load libraries}
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(zoo)
library(minpack.lm)
library(photobiologyWavebands)

@@

Moving this template to a working project folder will need editing of this file path to a relative path within the project folder.
```{r read ProcessFile}
ProcessFile <- "../Data/ImportedData/ImportedMCData/20211223_PICO_MCMIX006_RUN42_TargetDataMetaFilter.Rds"

>>>>

```{r load libraries}
# libraries; Note check actual dependencies

library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(zoo)
library(minpack.lm)
library(photobiologyWavebands)
library(tidyverse)

@@

Moving this template to a working project folder will need editing of this file path to a relative path within the project folder.
```{r read ProcessFile}
ProcessFile <- "../Data/ImportedData/ImportedMCData/20221021_PICO_MCMIX006_RUN96_TargetDataMetaFilter.Rds"
